Dirk Sliwka

### 2025-09-15 papers.qmd
Update

@@

*IZA Discussion Paper No. 16278*<br>
<a href="assets/pdf/PayEquity2023.pdf" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  PDF  </a>&nbsp;&nbsp;<button onclick="toggleAbstract('abstract-2023-Closing-the-Gender-Gap-in-Salary-Increases:-Evidence-from-a-Field-Experiment-on-Promoting-Pay-Equity')" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; background: none; display: inline-block;">Abstract</button>
<div id="abstract-2023-Closing-the-Gender-Gap-in-Salary-Increases:-Evidence-from-a-Field-Experiment-on-Promoting-Pay-Equity" style="display:none; border: 1px solid #ccc; padding: 10px; margin-top: 10px;">We present a natural field experiment on promoting pay equity through simple modifications to the salary review process in a large technology firm, involving 623 middle managers and 8,951 employees. Our treatments provided for a gender-blind reallocation of the salary increase budget available to middle managers aimed at pay equity, along with different variants of corresponding decision guidance. All treatments substantially reduced the gender gap in salary increases, going well beyond a purely mechanical effect of the budget reallocation. Moreover, the treatments do not appear to have undermined warranted performance differentiation in salary increases.</div>

>>>>

**Shaping Habits in Organizations: A Field Experiment**<br>
<a href="https://leonhardgrabe.github.io/">Leonhard Grabe</a>, <a href="https://sites.google.com/view/saskia-opitz/startseite">Saskia Opitz</a>, <a href="#">Dirk Sliwka</a><br>
*Available at SSRN 5270947*<br>
<a href="assets/pdf/Habits.pdf" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  PDF  </a>&nbsp;&nbsp;<a href="https://dx.doi.org/10.2139/ssrn.5270947" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  WEB  </a>&nbsp;&nbsp;<button onclick="toggleAbstract('abstract-2025-Shaping-Habits-in-Organizations:-A-Field-Experiment')" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; background: none; display: inline-block;">Abstract</button>
<div id="abstract-2025-Shaping-Habits-in-Organizations:-A-Field-Experiment" style="display:none; border: 1px solid #ccc; padding: 10px; margin-top: 10px;">We investigate whether organizations can shape work habits through monetary incentives. In a field experiment with 829 service technicians in 15 firms, we randomly allocated half of the technicians in each firm to a treatment group receiving bonuses for regularly performing sales activities for 12 weeks. We find a significant increase in sales activities not only during but also after the incentive phase. Using data from a post-experimental survey, we compare different behavioral channels. We find no evidence for increased automaticity, human capital acquisition, or signals about task priorities, but strong evidence for the role of acquired taste: Technicians in the treatment group report higher levels of intrinsic motivation to perform sales activities even after the incentive has been discontinued.</div>
<a href="assets/pdf/PayEquity2023.pdf" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  PDF  </a>&nbsp;&nbsp;<button onclick="toggleAbstract('abstract-2025-Closing-the-Gender-Gap-in-Salary-Increases:-Evidence-from-a-Field-Experiment-on-Promoting-Pay-Equity')" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; background: none; display: inline-block;">Abstract</button>
<div id="abstract-2025-Closing-the-Gender-Gap-in-Salary-Increases:-Evidence-from-a-Field-Experiment-on-Promoting-Pay-Equity" style="display:none; border: 1px solid #ccc; padding: 10px; margin-top: 10px;">We present a natural field experiment on promoting pay equity through simple modifications to the salary review process in a large technology firm, involving 623 middle managers and 8,951 employees. Our treatments provided for a gender-blind reallocation of the salary increase budget available to middle managers aimed at pay equity, along with different variants of corresponding decision guidance. All treatments substantially reduced the gender gap in salary increases, going well beyond a purely mechanical effect of the budget reallocation. Moreover, the treatments do not appear to have undermined warranted performance differentiation in salary increases.</div>

@@
